Democracy, Public Support, and Measurement Uncertainty

### 2021-08-05 paper/dcpo_demsupport.Rmd
using moc plots throughout the paper

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  eval = FALSE,
  dpi = 300
)

@@

load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

@@

## Data Recollection and Incorporating Uncertainty
Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
Our replication data has differences in number of country-year surveys and in sample size.
Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].

@@

Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error. 
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

```{r compare_n, eval = TRUE}

@@

```{r pointAJPS, eval=TRUE}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r result-pureAJPS}
result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_clsUncertain <- glance(result[[1]])
  }

  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
})

names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
```

```{r result-expAJPS}
result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_dcpoUncertain <- glance(result[[1]])
  }

  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
```

```{r coefName-AJPS, eval=TRUE}
index_coefName <- c(
  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
  `plm::lag(theta, 1)` = "Support[t-1]",
  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}

type_model <-
  c("Original", "Uncertainty", "Uncertainty+Expanded Data")

result_ajpsPooled <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
      legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    # scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

```{r pointAPSR, eval=TRUE}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r result-pureAPSR}
result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_clsUncertainAPSR <- glance.plm(result[[1]])

  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
```

```{r result-expAPSR}
result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])

  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
})

names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
```

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",

    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",

    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",

    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",

    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    # `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10, eval = TRUE}
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

type_model <-
  c("Original", "Uncertainty", "Uncertainty+Expanded Data")

result_apsrPooled <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$pooled1[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_apsrRegime <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Institution Specified")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)), 
           type = factor(type, levels = c("Pooled", "Institution Specified")))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    ggtitle("DV: The Change of Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    facet_wrap( ~ type) + 
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term))))
    # Using expressions of underscore and greek letters
    # scale_color_gb(palette = "digitMixed")

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Numeric Results for Replicating Claassen 2020a {#fullAJPS}

```{r num-labelAJPS, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
)
```

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- purrr::map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

modelsummary(tb_result_cls,  
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>%

  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_pureAJPS) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

modelsummary(tb_result_pureAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_expAJPS) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

modelsummary(tb_result_expAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty and Expanded Data") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

# Numeric Results for Replicating Claassen 2020b {#fullAPSR}

>>>>

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300
)

@@

# load(here("data", "correct_cls_ajps.rda"))
# load(here("data", "correct_cls_apsr.rda")) 
# load(here("data", "expcor_cls_ajps.rda"))
# load(here("data", "expcor_cls_apsr.rda"))

@@

## Data Recollection and Incorporating Uncertainty

Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
Our replication data has differences in number of country-year surveys and in sample size.
Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].

@@

Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error. 
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

```{r compare_n}

@@

```{r pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r mocresult-pureAJPS, eval=FALSE}

```{r mocresult-expAJPS, eval=FALSE}

```{r formatResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))

result_ajpsPooled <- result_pooledAJPS %>% 
    filter(type == "Pooled")

result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))

result_ajpsRegime <- result_regimeAJPS %>%
    filter(type == "Pooled") %>% 
    mutate(type = "Regime Specified")

```{r coefName-AJPS}
index_coefName <- c(
    `Democracy\n (t-1)` = "Democracy[t-1]",
    `Democracy\n (t-2)` = "Democracy[t-2]",
    `Support\n (t-1)` = "Support[t-1]",
    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}

type_model <-
  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
      legend.title = element_blank()
    ) +
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier

load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r mocresult-pureAPSR, eval=FALSE}

```{r mocresult-expAPSR, eval=FALSE}

```{r formatResult-APSR}
# Pooled---------------------------------------

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

result_apsrPooled <- result_APSR1 %>% 
    filter(type == "ECM") %>% 
    mutate(type = "Pooled")

# Institution----------------------------------

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

result_apsrRegime <- result_RegAPSR1 %>% 
    filter(type == "ECM") %>% 
    mutate(type = "Institution Specified")

# Pooled-corruption------------------------------

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

# Institution Corruption--------------------------------

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )
```

```{r coefName-APSR}
index_coefName <- c(
    `Democratic Mood\n (t-1)` = "Support[t-1]",
    `Democratic Mood\n (t-2)` = "Support[t-2]",
    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
type_model <-
    c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
    mutate(
        term = index_coefName[term],
        term = factor(term, levels = unique(index_coefName)),
        type = factor(type, levels = c("Pooled", "Institution Specified"))
    )

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    ggtitle("DV: The Change of Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    facet_wrap(~ type) +
    scale_color_gb(palette = "digitMixed")

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Data Recollection and Control Uncertainty in Control Variables.
